\documentclass[10pt,a4paper]{extarticle}
\pagenumbering{gobble}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx}
\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\begin{document}
\begin{center}
    \begin{minipage}{\textwidth}
        \centering
        {\LARGE\textbf{Umut Albayrak}} \hspace{2pt} {\large{Backend Developer | Computer Engineering Student}}\\[10pt]
        \href{mailto:umutalbayrakk24@gmail.com}{umutalbayrakk24@gmail.com} \textbullet\
        \href{https://umutalbayrak.dev}{umutalbayrak.dev} \textbullet\
        \href{https://linkedin.com/in/umut-albayrak24}{linkedin.com/in/umut-albayrak24} \textbullet\
        \href{https://github.com/Umutalb}{github.com/Umutalb}
    \end{minipage}
\end{center}
\section{Summary}
Computer Engineering student specializing in backend development with C\# and ASP.NET Core. Skilled in building RESTful APIs, database design, and applying clean architecture principles. Experienced with Git, Firestore, and agile teamwork. Seeking to contribute as a Junior Backend Developer with a strong focus on performance, scalability, and security.
\section{Technical Experience}
\textit{DatingApp2025} \hspace{3cm} \textit{Backend Developer \& Scrum Master}\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Collaborated in a 5-member team project, taking dual role as Backend Developer and Scrum Master.
    \item Developed backend modules with ASP.NET Core Web API for authentication, reporting, matching, and notifications.
    \item Designed and implemented the connection between the backend and Google Firestore for data persistence.
    \item Facilitated sprint planning and daily stand-ups as Scrum Master, ensuring effective collaboration and task tracking.
    \item Collaborated with a frontend developer (React) and an AI team (Flask) to integrate the recommendation system and ensure smooth API usage.
    \item Contributed to API documentation and version control with GitHub to support team collaboration.
\end{itemize}
\vspace{0.5cm} 
\textit{PhoneBook} \hspace{3cm} \textit{C++ Console App}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Built with CRUD operations and File I/O using C++ and STL.
    \item Persisted data with \texttt{fstream} in CSV-like format for load/save reliability.
\end{itemize}
\vspace{0.5cm} 
\textit{JobApplicationChecker} \hspace{3cm} \textit{C++ Console App}\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Built a rule-based eligibility checker (age, driver’s license, university graduation).
    \item Implemented clear control flow with nested conditions and case-insensitive string checks.
    \item Focused on user prompts and error messaging to guide decisions in a simple hiring scenario.
\end{itemize}
\section{Skills}
\textbf{Programming Languages:} C\#, C++ \\
\textbf{Backend Frameworks \& Runtimes:} ASP.NET Core, Entity Framework Core, RESTful API Development \\
\textbf{Frontend:} HTML, CSS \\
\textbf{Databases:} MSSQL Server, Google Firestore \\
\textbf{Other:} Git, GitHub, REST API, Postman, Swagger \\
\textbf{Methodologies:} Scrum, Agile, Clean Architecture
\section{Education}
\textbf{Van Yuzuncu Yıl University} \hfill Van, Turkiye\\
\textit{B.Sc. in Computer Engineering} \hfill Oct 2023 -- Jun 2027\\
\section{Certificates}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item HackerRank C\# (Basic) Certification – 2025
\end{itemize}
\section{Languages}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Turkish – Native
    \item English – Elementary Proficiency
\end{itemize}
\end{document}
